Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-05-13 analysis/paper/paper.Rmd
Added citations and 4th author

---
title: "Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea"
author:
  - Gayoung Park: 
      email: gayoungp@uw.edu
      institute: [UofW]
      correspondence: true
  - Marlize Lombard:
      email: mlombard@uj.ac.za
      institute: [UofJ]
      correspondence: false
  - Ben Marwick:
      email: bmarwick@uw.edu
      institute: [UofW]
      correspondence: false
institute:
  - UofW: Department of Anthropology, University of Washington, Seattle. USA
  - UofJ: Palaeo-Research Institute, University of Johannesburg, South Africa

@@

Marlize Lombard: Conceptualization, Methodology, Formal analysis, Writing - Review & Editing, Supervision

@@

>>>>

---
title: "Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea"
author:
  - Gayoung Park: 
      email: gayoungp@uw.edu
      institute: [UofW]
      correspondence: true
  - Marlize Lombard:
      email: mlombard@uj.ac.za
      institute: [UofJ]
      correspondence: false
  - Ben Marwick:
      email: bmarwick@uw.edu
      institute: [UofW]
      correspondence: false
  - Donghee Chong:
      email: okidok2@khu.ac.kr
      institute: [UofK]
      correspondence: false

institute:
  - UofW: Department of Anthropology, University of Washington, Seattle. USA
  - UofJ: Palaeo-Research Institute, University of Johannesburg, South Africa
  - UofK: Kyung Hee University, South Korea

@@

Marlize Lombard: Conceptualization, Methodology, Writing - Review & Editing, Supervision

@@

Donghee Chong: Data curation, Review & Editing
